Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation

### 2019-06-23 code/98-paper/journal/manuscript.tex
update wrapper methods

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{FFS}{forward feature-selection}
	\acro{FS}{feature-selection}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{ML}{Machine-Learning}
	\acro{NDII}{Normalized Difference Infrared Index}
	\acro{NIR}{Near-Infrared}
	\acro{NRI}{Normalized Ratio Index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machine}
	\acro{TPR}{True Positive Rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}

@@

% Wrapper approach
\noindent Another approach to reduce the number of variables is to apply algorithms that are used for hyperparameter optimization such as "Random Search" or a "Generic Simulated Annealing".
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to "filters", no ranking is applied in this step.
Now the model is fitted on the data and the performance is evaluated.
A disadvantage of this approach is that hyperparameter tuning can only start after the feature-selection optimization has ended.
Hence, this method is very expensive because two optimization stages need to be run.
In science this approach is also referred to as "wrapper method" \citep{chandrashekar2014, kohavi1997}.
It was not considered in this work due to the expensive runtime.

% PCA
A third commonly used method is the "Principal Component Analysis" \citep{pearson1901, jolliffe2016}.
Here, the main components of the feature space are extracted and combined.
Usually the first two components are taken since these contain the major information of the covariates.
By using the (automatically estimated) explained variance of the main components, the model can rely on a few features containing the majority of information available in the data.
This enables a very cheap model fitting with a minimal loss of predictor information.
However, the resulting features used in the model do not relate anymore to the raw input variables since they are a combination of multiple covariates.
Interpretation is not possible anymore.

>>>>

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{FFS}{forward feature-selection}
	\acro{FS}{feature-selection}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{ML}{Machine-Learning}
	\acro{NDII}{Normalized Difference Infrared Index}
	\acro{NIR}{Near-Infrared}
	\acro{NRI}{Normalized Ratio Index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{PCA}{principal component analysis}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machine}
	\acro{TPR}{True Positive Rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}

@@

\noindent Other approaches to assess feature importance are so called "wrapper methods" and the \ac{PCA} \citep{das2001, jolliffe2016}.
A short introduction to both is given below.

% Wrapper approach
\noindent "Wrapper methods" \citep{chandrashekar2014, kohavi1997} apply algorithms that are used for hyperparameter optimization such as "Random Search" or "Generic Simulated Annealing".
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to "filters", no ranking is applied in this step.
Now the model is fitted on the data and the performance is evaluated.
This is done multiple times, depending on the defined stopping criteria set by the user (performance, runtime, evaluations).
A disadvantage of this approach is that hyperparameter tuning can only start after the feature-selection optimization has ended.
Hence, this method is very expensive because two optimization stages need to be run in sequential order.
"Wrapper methods" were not considered in this work due to the expensive runtime.

% PCA
A method that is very distinct from filters and wrappers is the "Principal Component Analysis" \citep{pearson1901, jolliffe2016}.
Here, the main components of the feature space are extracted and combined.
Usually the first two components are taken since these contain the major information of the covariates.
By using the (automatically estimated) explained variance of the main components, the model can rely on a few features containing the majority of information available in the data.
This enables a very cheap model fitting with a minimal loss of predictor information.
However, the resulting features used in the model do not relate anymore to the raw input variables since they are a combination of multiple covariates.
Interpretation is not possible anymore.
